Weather Data Integration and Assimilation System\\

### 2020-02-14 introduction/sec_3-outline.tex
Test with cref for the reference naming

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in Chapter \ref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics. Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.

>>>>

\section{Outline}
The rest of the thesis is organized as follows. Literature review is presented in \cref{ch:literature}, and discuss about the existing Weather Data Integration Systems such as \acrshort{lead}, \acrshort{fews}, \acrshort{madis}, and \acrshort{dias}. Solution approach with the proposed system architectures and adaptation with problem occurred are presented in Chapter \ref{ch:method}. It provides details about how the \acrshort{wdias} is design by following a microservice architecture and the date preprocessing capabilities of the system. Performance analysis is presented in Chapter \ref{ch:results}. Here we discuss experiment setup of the \acrshort{wdias} and analyze the observations with respect to performance metrics. Finally, in Chapter \ref{ch:summary}, we conclude and summarize the work and further discussed about the research limitations and future work.

### 2020-02-14 lit/sec_1-fews.tex
Updates from Overleaf
Test with cref for the reference naming

Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts. %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. 
Other countries are also using those systems while adopting them %with own version of system which effective for the 
to specific weather condition.% in a particular country.
This chapter presents a literature review on existing systems and their architecture approach and design. In Section \ref{se:fews}, we present \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}. % \acrshort{lead} is following the \acrfull{soa} for system architecture. 
In Section \ref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in Section \ref{se:madis}.
Under each system we explore both system architecture, scalability, and flexibility of the system.

@@

In \db{Figure} \ref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
\dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
\gkc{FIXED}

@@

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the {application programming interface (API)}. It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in \acrshort{fews}, users do not ave the capability to take the advantage of such existing things.
\dbc{Define Abb. for API in Chapter 1.}

>>>>

Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts. %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. 
Other countries are also using those systems while adopting them %with own version of system which effective for the 
to specific weather condition.% in a particular country.
This chapter presents a literature review on existing systems and their architecture approach and design. In \cref{se:fews}, we present \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in Section \ref{se:lead}. % \acrshort{lead} is following the \acrfull{soa} for system architecture. 
In Section \ref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in Section \ref{se:madis}.
Under each system we explore both system architecture, scalability, and flexibility of the system.

@@

In \db{Figure} \cref{fi:fews_schematic} show a schematic view of the connection between the forecasting system to real time data acquisition systems and dissemination systems. The widely using concept is using meteorological forecast data to get precipitation and, then using hydrological and hydraulic model chain to predict the level affect on the ground. The hydrological and hydraulic model should be design based on the ground. Basically ground should be analyze geographically and divide into the catchments. Based on the affected catchment, it can be further divide into sub areas to reduce the complexity of the simulation task. Ideally the forecasting system should therefore be flexible to allow change to models and data, while keeping the way forecasters work with it as constant as possible.
\dbc{F is capital and T is capital when referring to Figures and Tables. Fix all other places.}
\gkc{FIXED}

@@

Data processing and manipulation is a required process in weather forecasting. Most of the data that is imported from external sources is not at the appropriate temporal and spatial scale to be applied as an input to a forecasting model, or to be used directly in product generation. As a consequence, generic data processing steps form the predominant effort in most applications of models in the forecast environment. Some examples include data validation, serial and spatial interpolation, aggregation and dis-aggregation, and merging data \cite{Werner2013TheSystem}. This a vital feature in a forecasting system, and affect on the quality and accuracy of the predicted data outputs. Because of the common data model concept in \acrshort{fews}, data processing via these function is much effective. The system is self provided some of the generic functions for data processing, but for more complex algorithms can be developed as a new Java class coded to communicate with the {application programming interface (API)}. It is obvious that for additional feature integration, user should implement the new functional extensions via Java programming language. Users does not have the flexibility of develop with some other languages they are familiar with or use the support from another language. As an example, Python language is easy to use for beginners and many of data scientists are using this programming language for development and it has many data available libraries for data processing. But in \acrshort{fews}, users do not have the capability to take the advantage of such existing things.
\dbc{Define Abb. for API in Chapter 1.}
